\LARGE How coexistence mechanisms mediate temporal stability

### 2016-03-15 manuscript/manuscript.Rmd
adds new storage effect strngth plot

For biodiversity to increase the temporal stability of ecosystem function in the long-term, coexistence must be stable.
Species-specific respones to environmental variation through time is key to understanding fluctuation-dependent coexistence mechanisms and how asynchrony in species dynamics can arise to stabilize ecosystem function.
Despite the shared dependence on environmental fluctuations, theory on species coexistence and the relationship between species richness and ecosystem stability have developed independently.
To formally link the two bodies of theory, we use consumer-resource models where coexistence between two species utilizing a single resource is maintained by two fluctuation-dependent mechanisms: the storage effect and relative nonlinearity.
We examine how the strength of species coexistence relates to the temporal stability of aggregate ecosystem function and how the effect of environmental variability on stability is mediated by the mechanism of coexistence.
When species coexisted via the storage effect, the strength of coexistence, as measured by invasion growth rates, was `blank` associated with ecosystem variability (rank correlation = ).
On the other hand, ecosystem variability and the strength of coexistence were `blank` associated under relative nonlinearity (rank correlation = ) because the ability of an inferior competitor to persist increases with resource variability.
Total community biomass was always less variable when species coexisted via the storage effect rather than relative nonlinearity.
Our analysis confirms the intuitive idea that stable coexistence and stable ecosystems go hand-in-hand, but only for the storage effect.
However, coexistence by relative nonlinearity is likely to be less common in nature, meaning our results from storage effect simulations may be most relevant to field studies.

@@

Model and Analysis
------------------------------
### A General Consumer-Resource Model

@@

### Model Simulations
For each coexistence mechanism (storage effect, relative nonlinearity), we ran model simulations at different levels of resource variance ($R_{\sigma^2}$), environmental cue variance ($\sigma_E$), and correlation of species responses to the environmental cue ($\rho$). 
We ran simulations for 100 'seasons' with 60 day growing seasons. 
We averaged biomass over the growing season.
After discarding an initial 100 seasons to reduce transient effects on our results, we calculated the stability of summed species biomass through time and species synchrony through time.
For storage effect simulations, species were equivalent in their ability to capture and assimilate the resource (*R*) but had different, depending on $\rho$, germination rates.
For relative nonlinearity simulations, species had equivalent germination rates ($\rho = 1$) but different resource acquisition functions (fig. 1).
We explored a limited set of parameter space where the storage effect and relative nonlinearity were operating simultaneously.
Within-season dynamics were solved given initial conditions using the package 'deSolve' [@Soetaert2010] in R [@Team2013].

Results
-------

>>>>

For biodiversity to increase the temporal stability of ecosystem function in the long-term, coexistence must be stable.
Species-specific respones to environmental variation through time is key to understanding fluctuation-dependent coexistence mechanisms and how asynchrony in species dynamics can arise to stabilize ecosystem function.
Despite the shared dependence on environmental fluctuations, theory on species coexistence and the relationship between species richness and ecosystem stability have developed independently.
To formally link the two bodies of theory, we use consumer-resource models where coexistence between two species utilizing a single resource is maintained by two fluctuation-dependent mechanisms: the storage effect and relative nonlinearity.
We examine how the strength of species coexistence relates to the temporal stability of aggregate ecosystem function and how the effect of environmental variability on stability is mediated by the mechanism of coexistence.
Blah, blah, blah...

@@

Model and Analysis
------------------
### A General Consumer-Resource Model

@@

### Model Simulations
For each coexistence mechanism (storage effect, relative nonlinearity), we ran model simulations at different levels of resource variance ($R_{\sigma^2}$), environmental cue variance ($\sigma_E$), and correlation of species responses to the environmental cue ($\rho$). 
We ran simulations for 100 'seasons' with 60 day growing seasons. 
We averaged biomass over the growing season.
After discarding an initial 20 seasons to reduce transient effects on our results, we calculated the stability of summed species biomass through time and species synchrony through time.
For storage effect simulations, species were equivalent in their ability to capture and assimilate the resource (*R*) but had different, depending on $\rho$, germination rates.
For relative nonlinearity simulations, species had equivalent germination rates ($\rho = 1$) but different resource acquisition functions (fig. 1).
We explored a limited set of parameter space where the storage effect and relative nonlinearity were operating simultaneously.
Within-season dynamics were solved given initial conditions using the package 'deSolve' [@Soetaert2010] in R [@Team2013].

Results
-------
The strength of coexistence is negatively associated with ecosystem variability when species coexistence is maintained by the storage effect (fig. 2).

\begin{figure}[!ht]
  \centering
      \includegraphics{./components/storage_effect_growthrate_cv.png}
  \caption{Relationship between the strength of coexistence (invasion growth rate of inferior competitor) and ecosystem variability. Panels show different levels of environmental cue variability (denoted by number at top of each panel). Color bar shows the correlation between species' germination rates.}
\end{figure}
